Hydra Battles and Cie

### 2021-09-03 doc/part-hydras.tex
Corrections Chapter 5

\input{movies/snippets/Epsilon0_Needed_Free/mGe}

@@

 We build the following paths :

 \begin{enumerate}
 \item $\alpha \xrightarrow[n]{} \canonseq{\alpha}{n}$
 \item $\canonseq{\alpha}{n} \xrightarrow[1]{} \canonseq{\alpha}{i}$ (by \texttt{Theorem\_2\_4}),
\item $\canonseq{\alpha}{n} \xrightarrow[n]{} \canonseq{\alpha}{i}$ (applying the induction hypothesis to the preceding path);
\item $\canonseq{\alpha}{i} \xrightarrow[n]{} \beta$ (applying the induction hypothesis)\item $\alpha \xrightarrow[n]{} \beta$ (by composition of 1, 3, and 4).

@@

The article~\cite{KS81} contains 
the following lemma, the proof of which is quite complex, which allows to simulate $i$-paths by $[i+1,j]$-paths, where $j$ is large enough.

@@

\begin{itemize}
\item If $\beta=\gamma$, its OK! We have got a standard path
from  
$\alpha$ to $\beta$ with successive indices  $n+1, n+2, \dots, n+l+1$

@@

\input{movies/snippets/Paths/constantToStandard0}

@@

Next, please consider the following context:

>>>>

\inputsnippets{Epsilon0_Needed_Free/mGe}

@@

The proof of the limit case, is decomposed into a sequence
of path constructions leading to $\alpha \xrightarrow[n]{} \beta$.

 \begin{enumerate}
 \item $\alpha \xrightarrow[n]{} \canonseq{\alpha}{n}$ (single step path)
 \item $\canonseq{\alpha}{n} \xrightarrow[1]{} \canonseq{\alpha}{i}$ (by \texttt{Theorem\_2\_4}),
\item $\canonseq{\alpha}{n} \xrightarrow[n]{} \canonseq{\alpha}{i}$ (applying the induction hypothesis to the preceding path);
\item $\canonseq{\alpha}{i} \xrightarrow[n]{} \beta$ (applying the induction hypothesis)
\item $\alpha \xrightarrow[n]{} \beta$ (by composition of 1, 3, and 4).

@@

The article~\cite{KS81} contains 
the following lemma, which allows us to simulate $i$-paths by $[i+1,j]$-paths, where $j$ is large enough.

@@

\begin{itemize}
\item If $\beta=\gamma$, it's OK! We have got a standard path
from  
$\alpha$ to $\beta$ with successive indices  $n+1, n+2, \dots, n+l+1$

@@

 \input{movies/snippets/Paths/constantToStandard0}
 \input{movies/snippets/Paths/constantToStandardz}

@@

Now, please consider the following context:
